---
title: "Red Bluff Diversion Dam Database Data Pull"
output: html_document
date: "2022-09-02"
---

This document queries the RBDD database provided by Bill Poytress to extract
RST data for the upper sac Red Bluff Diversion Dam RST. 

If this file doesn't run, make sure operating system is being set correctly. 
Depending on the operating system this script will run either the query_rbdd_database
'4pc' or '4mac'


```{r, include = F}
library(tidyverse)
library(knitr)
library(lubridate)
library(googleCloudStorageR)
library(Hmisc)
root.dir <- rprojroot::find_rstudio_root_file()
knitr::opts_knit$set(root.dir)
```


# Pull in Access tables (see pull data script)


# Trap
```{r}
trap_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/trap_access_post_2012.csv")
trap_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/trap_access_pre_2012.csv")

# TODO followup on the following for trap 
# TODO figure out whtat is going on with stations vs sites 
# TODO check on diel = do we need if we have time? What are the C or unlettered values stand for 
# TODO how does sample weighting work - it sounds like this is all based on total hours sampled in sample period is this correct. Should catch be scaled according to this sample weight
trap_visit <- bind_rows(trap_pre_2012, trap_post_2012) |> 
  mutate(site = "red bluff",
         fish_properly = ifelse(fish_properly == "Y", TRUE, FALSE),
         weather = case_when(weather_code == "CLD" ~ "cloudy", 
                             weather_code == "CLR" ~ "clear", 
                             weather_code == "FOG" ~ "foggy", 
                             weather_code == "RAN" ~ "rainy", 
                             weather_code == "W" ~ "windy"),
         gear_condition = case_when(tolower(gear_condition) == "n" ~ "normal", 
                                   tolower(gear_condition) == "pb" ~ "partial block",
                                   tolower(gear_condition) == "tb" ~ "total block",
                                   tolower(gear_condition) %in% c("n/p", "nr") ~ "not recorded",)) |> 
  select(-weather_code) |> glimpse()

table(trap_visit$subsite)
table(trap_visit$trap_sample_type)
table(trap_visit$diel)
# Save data to google cloud
write_csv(trap_visit, "data-raw/database_tables_pulled_by_flowwest/rbdd_trap_raw_combined.csv")
```

# Catch
```{r}
catch_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/catch_access_post_2012.csv")
catch_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/catch_access_pre_2012.csv")

# TODO followup on the following for catch
# TODO mark_code = Ad_pelvic - is this important? Signifies winter run out of Battle Creek - We would want to contain this information add additional column to do add_pelvic true or false 
# TODO confirm catch is added across traps - trap is summed accross a trap before it is summed across traps for a certain day (wouln't want to expand some of that subsampling info across traps) - keeps info on different effort across traps 
catch <- bind_rows(catch_pre_2012, catch_post_2012) |> 
  mutate(site = "red bluff",
         dead = ifelse(tolower(dead) == "yes", TRUE, FALSE),
         run = case_when(run == "F" ~ "fall run", 
                         run == "L" ~ "late fall run", 
                         run == "S" ~ "spring run", 
                         run == "W" ~ "winter run",
                         run == "n/p" ~ "not recorded"),
         adipose_clipped = ifelse(mark_code == "Adclipped", TRUE, FALSE),
         weight = ifelse(weight == 0, NA, weight),
         fork_length = ifelse(fork_length == 0, NA, fork_length)) |> 
  select(-mark_code) |> glimpse()

table(catch$mark_code)
# Save combined data
write_csv(catch, "data-raw/database_tables_pulled_by_flowwest/rbdd_catch_raw_combined.csv")
```

# Releases 
```{r}
release_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_access_post_2012.csv")
release_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_access_pre_2012.csv")

# TODO followup on the following for release
# TODO figure out whtat is going on with stations vs sites vs gages
release <- bind_rows(release_pre_2012, release_post_2012) |> 
  mutate(site = "red bluff") |> glimpse()

# recaptured fish 
release_fish_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_fishaccess_post_2012.csv")
release_fish_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_fishaccess_pre_2012.csv")

# TODO how do I link these to a release ID? Looks like release id is present in database but the mdb.get function turns them all na
release_fish <- bind_rows(release_fish_pre_2012, release_fish_post_2012) |> 
  mutate(site = "red bluff",
         dead = ifelse(tolower(dead) == "yes", TRUE, FALSE))|> glimpse()

write_csv(release, "data-raw/database_tables_pulled_by_flowwest/rbdd_releases_raw.csv")
write_csv(release_fish, "data-raw/database_tables_pulled_by_flowwest/rbdd_release_fish_raw.csv")

```

# Recaptures 
```{r}
# TODO ideally I would combine these 2 tables but no id to join on 
# recaps metadata table 
recaps_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_access_post_2012.csv")
recaps_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_access_pre_2012.csv")

# TODO followup on the following for recaps
# TODO figure out whtat is going on with stations vs sites 

recapture <- bind_rows(recaps_pre_2012, recaps_post_2012) |> 
  mutate(site = "red bluff",
         gate = tolower(station_code)) |> 
  select(-station_code) |> glimpse()

# recaptured fish 
recapture_fish_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_fishaccess_post_2012.csv")
recapture_fish_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_fishaccess_pre_2012.csv")

# TODO how do I link these to a release ID? 
recapture_fish <- bind_rows(recapture_fish_pre_2012, recapture_fish_post_2012) |> 
  mutate(site = "red bluff",
         dead = ifelse(tolower(dead) == "yes", TRUE, FALSE))|> glimpse()

recapture_table <- full_join(recapture, recapture_fish, 
                             by = c("recapture_row_id" = "recap_row_id", "site" = "site")) |> glimpse()

table(recapture$station_code)
write_csv(recapture_table, "data-raw/database_tables_pulled_by_flowwest/rbdd_recaptures_raw.csv")

```
