---
title: "Red Bluff Diversion Dam Database Data Pull"
output: html_document
date: "2022-09-02"
---

This document queries the RBDD database provided by Bill Poytress to extract
RST data for the upper sac Red Bluff Diversion Dam RST. 

If this file doesn't run, make sure operating system is being set correctly. 
Depending on the operating system this script will run either the query_rbdd_database
'4pc' or '4mac'


```{r, include = F}
library(tidyverse)
library(knitr)
library(lubridate)
library(googleCloudStorageR)
library(Hmisc)
root.dir <- rprojroot::find_rstudio_root_file()
knitr::opts_knit$set(root.dir)
```


# Pull in Access tables (see pull data script)


# Trap
```{r}
trap_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/trap_access_post_2012.csv") |> glimpse()
trap_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/trap_access_pre_2012.csv") |> glimpse()

trap_visit <- bind_rows(trap_pre_2012, trap_post_2012) |> 
  mutate(weather = case_when(weather_code == "CLD" ~ "cloudy", 
                             weather_code == "CLR" ~ "clear", 
                             weather_code == "FOG" ~ "foggy", 
                             weather_code == "RAN" ~ "rainy", 
                             weather_code == "W" ~ "windy"),
         gear_condition = case_when(tolower(gear_condition) == "n" ~ "normal", 
                                   tolower(gear_condition) == "pb" ~ "partial block",
                                   tolower(gear_condition) == "tb" ~ "total block",
                                   tolower(gear_condition) == "nr" ~ "not rotating",
                                   tolower(gear_condition) %in% c("n/p") ~ "not recorded"),
        river_depth = ifelse(river_depth > 9, 99, river_depth),
        station_code = tolower(station_code), 
        temperature = ifelse(temperature > 1000, NA, temperature)) |> 
  select(-weather_code) |> glimpse()

table(trap_visit$subsite)
table(trap_visit$trap_sample_type)
table(trap_visit$diel)
hist(trap_visit$river_depth)
table(trap_visit$gear_condition)
hist(trap_visit$temperature)
# Save data to google cloud
write_csv(trap_visit, "data-raw/database_tables_pulled_by_flowwest/rbdd_trap_raw_combined.csv")
```

# Catch
```{r}
catch_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/catch_access_post_2012.csv") |> glimpse()
catch_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/catch_access_pre_2012.csv") |> glimpse()
summary(catch_pre_2012)
summary(catch_post_2012)

catch <- bind_rows(catch_pre_2012, catch_post_2012) |> 
  mutate(dead = ifelse(tolower(dead) == "yes", TRUE, FALSE),
         run = case_when(run == "F" ~ "fall run", 
                         run == "L" ~ "late fall run", 
                         run == "S" ~ "spring run", 
                         run == "W" ~ "winter run",
                         run == "n/p" ~ "not recorded"),
         ad_pelvic = ifelse(mark_code == "Ad_pelvic", TRUE, FALSE),
         adipose_clipped = case_when(mark_code == "Adclipped" ~ TRUE,
                                     ad_pelvic ~ TRUE, 
                                     T ~ FALSE),
         weight = ifelse(weight == 0, NA, weight),
         fork_length = ifelse(fork_length == 0, NA, fork_length),
         station_code = tolower(station_code)) |> 
  select(-mark_code) |> glimpse()

table(catch$mark_code)
# Save combined data
write_csv(catch, "data-raw/database_tables_pulled_by_flowwest/rbdd_catch_raw_combined.csv")
```

# Releases 
```{r}
release_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_access_post_2012.csv") |> glimpse()
# REmove pre because duplicates of post
# release_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_access_pre_2012.csv") |> glimpse()
summary(release_post_2012)
# summary(release_pre_2012)

release <- release_post_2012 |> 
  mutate(excluded = ifelse(excluded == "N", FALSE, TRUE),
         gates = tolower(gates)) |> 
  select(-comments) |> glimpse()

# recaptured fish 
release_fish_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_fishaccess_post_2012.csv") |> glimpse()
# remove pre because duplicates of post
# release_fish_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/release_fishaccess_pre_2012.csv") |> glimpse()

release_fish <- release_fish_post_2012 |> 
  mutate(dead = ifelse(tolower(dead) == "yes", TRUE, FALSE),
         fish_origin = tolower(fish_origin),
         source = tolower(source))|> glimpse()

write_csv(release, "data-raw/database_tables_pulled_by_flowwest/rbdd_releases_raw.csv")
write_csv(release_fish, "data-raw/database_tables_pulled_by_flowwest/rbdd_release_fish_raw.csv")

```

# Recaptures 
```{r}
# recaps metadata table 
recaps_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_access_post_2012.csv") |> glimpse()
# All pre values appear to be duplicates
# recaps_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_access_pre_2012.csv") |> glimpse()

recapture <- recaps_post_2012 |> 
  mutate(station_code = tolower(station_code)) |> glimpse()

# recaptured fish 
recapture_fish_post_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_fishaccess_post_2012.csv") |> glimpse()
# All pre values appear to be duplicates
# recapture_fish_pre_2012 <- read_csv("data-raw/database_tables_pulled_by_flowwest/recapture_fishaccess_pre_2012.csv") |> glimpse()

recapture_fish <- recapture_fish_post_2012 |> 
  mutate(dead = ifelse(tolower(dead) == "yes", TRUE, FALSE))|> glimpse()

recapture_table <- left_join(recapture_fish, recapture, 
                             by = c("mark_recap_id" = "recapture_row_id" )) |> 
  select(mark_recap_id = recap_row_id, trial_id, sample_date, sample_time, station_code, flows, mark_code, fork_length, count, dead) |> 
  filter(!is.na(sample_date)) |> 
  glimpse()

summary(recapture_table)
table(recapture$station_code)
write_csv(recapture_table, "data-raw/database_tables_pulled_by_flowwest/rbdd_recaptures_raw.csv")

```
